DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-12 paper/core/exp_setup.tex
added discussion and results section
added abstract
added extra evaluation figure

\begin{figure}[hp]
    \centering
    \includegraphics[width=0.45\textwidth]{diagrams/framework}
    \caption{The training framework of DeepSched network. A database of tasks and resources is provided for both network and HEFT. The loss of the network is measured based on HEFT produced schedule.}
    \label{fig:fw}
\end{figure}

>>>>

\begin{figure}[hp]
    \centering
    \includegraphics[width=0.45\textwidth]{diagrams/train_framework}
    \caption{The training framework of DeepSched network. A database of tasks and resources is provided to both network and HEFT. The loss of the network is measured based on HEFT produced schedule.}
    \label{fig:fw}
\end{figure}

\begin{figure}[hp]
    \centering
    \includegraphics[width=0.45\textwidth]{diagrams/eval_framework}
    \caption{The evaluation framework of DeepSched network. A database of tasks and resources is provided to all three schedulers. The output schedules are passed to a simulation stub, which runs the schedules and calculates average turnaround time.}
    \label{fig:efw}
\end{figure}
